Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-08-07 Introduction.tex
Figures & text
Obviously

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may well map to a plurality of games, this still allows for a principled comparison between interpretations and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. Where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement, this is clearly desirable.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem. In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.

>>>>

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may well map to a plurality of games, this still allows for a principled comparison between interpretations and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem. In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.

### 2014-08-07 Methods.tex
Figures & text
Obviously

Two key measures were used - the fraction of the subpopulation who had ever signalled honestly, and the proportion referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

@@

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w}\,\&\,w_{w}={0.25, 0.5, 0.75, 1}\).

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.

@@

To better capture the response characteristics for the model, we measure three outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs. Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.

Measurements were taken at the end of 1000 rounds of play, and for 1 and 2, 400 results were selected covering the full hypercube with each chosen randomly from the runs for that design point. This approach, rather than averaging across runs, was taken to avoid obscuring the high degree of variability evident in the output of the payoff reasoning agents in some areas of the parameter space.

Twelve emulators were built, covering each of the three output on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

@@

\begin{table}
\center
\begin{tabular} {| l | l |}
Name & Description \\ \hline

\end{tabular}
\caption[Table caption text]{Output measures. \label{tab:sa_measures}}
\end{table}

>>>>

Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

@@

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w}=w_{w}={0.25, 0.5, 0.75, 1}\), with 100 runs under each condition.

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. Under this method...

@@

To better capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs. Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).

Measurements were taken at the end of 1000 rounds of play, and emulators were built against the mean, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.

Twelve emulators were built, covering each of the four output on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

@@

### 2014-08-07 Results.tex
Figures & text
Obviously

\begin{figure}[h!]
\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot.png}

}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot.png}}\end{adjustbox}
\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs.}
\label{fig:qt_trends}
\end{figure}

@@

@@

The full results for the sensitivity analysis covering all twelve emulators are available in appendix \ref{}, and in this section we present selected results highlighting......

>>>>

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot}

}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot}}\end{adjustbox}
\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs.}
\label{fig:qt_trends}
\end{figure}

@@

Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.

Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the .25 level, and the associated increase in false positives. This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal. The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.

The relationship is not, however entirely that simple, in that increasing information sharing leads to greater variance between runs. A linear model was was used to predict the standard deviation between runs of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis.

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Honest signalling\label{fig:honest_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_sharing}

}\subfloat[Referrals\label{fig:ref_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/ref_sharing}}\end{adjustbox}
\caption{Impact of information sharing on qualitative trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
\label{fig:sharing_trends}
\end{figure}

@@

In this section we present selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women. The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{}

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Mean moderate drinker signal vs mean between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}
